Proposed Solution

### 2016-11-14 Ennan-Proposal/solutions.tex
clarify thresholds

We now describe a formalism how to compute the set of learned
probabilistic rules, denoted by $\mathcal{PR}$.
With $\mathcal{U}$ we denote a set of configuration files in the 
intermediate representation. If a template can be instantiated with
keywords from file $f$ and the obtained rule $r$ holds, we state that with the predicate 
$\mathit{appears}(r,f)$.
If a template is instantiated and we obtain rule $r$, with  the predicate 
$\mathit{holds}(r,f)$ we state that either predicate $\mathit{appears}(r,f)$ holds, or 
$r$ could not be instantiated with keywords from $f$ (namely, rule $r$ is irrelevant 
for $f$ and then trivially holds). With every 
rule $r$ we define two sets:
\begin{align*}
S_A(r)& =\{ \ f \in \mathcal{U}\ | \ \mathit{appears}(r,f)\  \} \\
S_H(r)& =\{ \ f \in \mathcal{U}\  | \ \mathit{holds}(r,f) \ \}
\end{align*}
We define then set $\mathcal{PR}$ as
$$\mathcal{PR} = \{\ r \ \mid \ |S_A(r)| > T_1 \land |S_H(r)| > T_2 \ \} $$
where $T_1$ is a threshold value for considering rules which are true in 
majority of cases, and $T_2$ is a threshold value for considering rules 
for which there is sufficiently enough files where the rule
appears. Finding the exact values of $T_1$ and $T_2$ is 
and their connection to $|\mathcal{U}|$
is a question still to be solved.
Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
We plan to try multiple strategies to find these values.
One approach may be to use machine learning for program autotuning, with a tool like OpenTuner~\cite{ansel:pact:2014}.
This requires creating some cost function for which the autotuning can optimize.
Additionally, it is possible that $T_1$ and $T_2$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
Building a clear formalization and a modular tool to explore these questions is major task.

>>>>

We now describe a formalism how to compute the set of learned
probabilistic rules, denoted by $\mathcal{PR}$.
With $\mathcal{U}$ we denote a set of configuration files in the 
intermediate representation. If a template can be instantiated with
keywords from file $f$ and the obtained rule $r$ holds, we state that with the predicate 
$\mathit{appears}(r,f)$.
If a template is instantiated and we obtain rule $r$, with  the predicate 
$\mathit{holds}(r,f)$ we state that either predicate $\mathit{appears}(r,f)$ holds, or 
$r$ could not be instantiated with keywords from $f$ (namely, rule $r$ is irrelevant 
for $f$ and then trivially holds). With every 
rule $r$ we define two sets:
\begin{align*}
S_A(r)& =\{ \ f \in \mathcal{U}\ | \ \mathit{appears}(r,f)\  \} \\
S_H(r)& =\{ \ f \in \mathcal{U}\  | \ \mathit{holds}(r,f) \ \}
\end{align*}
We define then set $\mathcal{PR}$ as
$$\mathcal{PR} = \{\ r \ \mid \ |S_A(r)| > T_1 \land |S_H(r)|/|\mathcal{U}| > T_2 \ \} $$
We use $T_1$ to act as an integer threshold value so any accepted rule must appear in sufficiently enough files where the rule appears. 
We use $T_2$ to act as a percentage threshold value so that any accepted rule must be true in a majority of cases. 
Finding the exact values of $T_1$ and $T_2$
and their connection to $|\mathcal{U}|$
is a question still to be solved.
Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
We plan to try multiple strategies to find these values.
One approach may be to use machine learning for program autotuning, with a tool like OpenTuner~\cite{ansel:pact:2014}.
This requires creating some cost function for which the autotuning can optimize.
Additionally, it is possible that $T_1$ and $T_2$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
Building a clear formalization and a modular tool to explore these questions is major task.
